### 2018-07-22 sections/signal_background_modeling.tex
v0.3 of paper draft

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to \textsc{Pythia} 8.212~\cite{Sjostrand:2007gs} for parton showering and fragmentation. 
The A14~\cite{ATLASUETune4} set of tuned parameters in \textsc{Pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
Parton shower and hadronisation are modelled by {\textsc Pythia}~8.2 with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} set of PDFs. 
The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5f FFN~\cite{Ball:2012cx} PDF sets.

@@

Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.3.2, using 
NLO matrix elements and the NNPDF3.0 NLO~\cite{Ball:2014uwa} PDF set. 
Showering is performed using {\pythia}~8.210 and the A14 tune.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}.
The $\ttbar H$ sample is normalised using the NLO cross section~\cite{Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}  
and the Higgs boson decay branching ratios calculated using \textsc{Hdecay}.

%The production of four-top-quark events in the SM was simulated by samples generated at LO using {\amcatnlo}~2.2.2
%and the NNPDF2.3 LO PDF set, interfaced to {\pythia} 8.186 in combination with the A14 tune. 
%The sample was normalised to a cross section of 9.2 fb, computed at NLO~\cite{Alwall:2014hca}.

All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~v1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pileup, events from minimum-bias interactions are generated using the \textsc{Pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

>>>>

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} for parton showering and fragmentation. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
Parton shower and hadronisation are modelled by {\pythia}~8.2 with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} set of PDFs. 
The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5f FFN~\cite{Ball:2012cx} PDF sets.

@@

Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.~.2, using 
NLO matrix elements and the NNPDF3.0 NLO~\cite{Ball:2014uwa} PDF set. 
Showering is performed using {\pythia}~8.210 and the A14 tune.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}.
The $\ttbar H$ sample is normalised using the NLO cross section~\cite{Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}  
and the Higgs boson decay branching ratios calculated using \textsc{Hdecay}.

%The production of four-top-quark events in the SM was simulated by samples generated at LO using {\amcatnlo}~2.2.2
%and the NNPDF2.3 LO PDF set, interfaced to {\pythia}~8.186 in combination with the A14 tune. 
%The sample was normalised to a cross section of 9.2 fb, computed at NLO~\cite{Alwall:2014hca}.

All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~v1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pileup, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

### 2018-07-22 sections/systematic_uncertainties.tex
v0.3 of paper draft

Uncertainties affecting the modelling of the single-top-quark background include a 
$+5\%$/$-4\%$ uncertainty in the total cross section estimated as a weighted average 
of the theoretical uncertainties in $t$-, $Wt$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
samples with alternative samples where generator parameters are varied.
For the $t$- and $Wt$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
by comparing events produced by {\powheg} interfaced to {\pythia} 6 or {\herwigpp}.
These uncertainties are treated as fully correlated among single-top production processes, but uncorrelated with the
corresponding uncertainty in the $\ttbar$+jets background.
An additional systematic uncertainty on $Wt$-channel production concerning the separation 
between $t\bar{t}$ and $Wt$ at NLO is assessed by comparing
the nominal sample, which uses the so-called ``diagram removal'' scheme~\cite{Frixione:2008yi}, with an alternative sample
using the ``diagram subtraction'' scheme~\cite{Frixione:2008yi}.

>>>>

Uncertainties affecting the modelling of the single-top-quark background include a 
$+5\%$/$-4\%$ uncertainty in the total cross section estimated as a weighted average 
of the theoretical uncertainties in $t$-, $Wt$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
samples with alternative samples where generator parameters are varied.
For the $t$- and $Wt$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
by comparing events produced by {\powheg} interfaced to {\pythia}~6 or {\herwigpp}.
These uncertainties are treated as fully correlated among single-top production processes, but uncorrelated with the
corresponding uncertainty in the $\ttbar$+jets background.
An additional systematic uncertainty on $Wt$-channel production concerning the separation 
between $t\bar{t}$ and $Wt$ at NLO is assessed by comparing
the nominal sample, which uses the so-called ``diagram removal'' scheme~\cite{Frixione:2008yi}, with an alternative sample
using the ``diagram subtraction'' scheme~\cite{Frixione:2008yi}.
